A Sample {\ttlit ACM} SIG Proceedings Paper in LaTeX Format\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}

### 2014-03-03 draft.tex
Design principles extraction

The second class of issues concerns platform integrity and user data privacy. In parituclar, the security architecture of those platform normally do not provide high assurance of privacy. Morevoer, from the point of a cloud provider, it is difficult to observe and inspect deeply the functioning of the whoe platform, leveraging commodity general purpose hypervisors (GPH).
General Purpose Hypervisors are executed at the most privileged level and so, it is complicated to detect and intervene on them in presence of malicious attack or misbehavior, without service interruption for all VMs hosted on the server. Cloudvisor \cite{cloudvisor:zhang} analyzed the problem proposing a nested architecture, where the GPH is executed at a lower level of privilege and a tiny hypervisor, responsible to prevent data disclosure, is executed at Ring 0.Hence, this kind of requirements could be called vertical requirements, because they involves layers executed at different layer of the software architecture.

To sum up, nested virtualization has shown to be a interesting pattern for modern cloud platform, that could improve dramatically features and integrity of cloud platform. However, no architecture had been presented to address vertical and horizontal class of problems at the same time. XenBlanket does not investigate cloud security concerns, limiting the focus on new potential feature of a coordinated multi-provider cloud. Cloudvisor proposed a security architecture that leverages nested virtualization without allowing the possibility of executing more than one nested hypervisor at time, that is a crucial requirements of a multi-provider cloud platform.

In this paper, we will present a nested architecture 
% Name?
that address this two different horizontal and vertical kind of issues at the same time.

\section{Related Work}
Cloud computing feature set could be enlarged exploiting two layers of virtualization instead of just one. The presence of two different hypervisors allows the possibility to specialize hypervisors functions. Instead of having a general purpose hypervisor we could split task in two different layers, interconnected with a well defined interface.
Each layer will have to care about a subset of feautures, simplifying overall development.

@@

\section{Nested Virtualization}

Recursive virtualization} refers to a system architecture with several layers of virtualization. It consists in a ``virtualized'' virtualization, where the guest system virtualize a nested guest. The concept could be generalized to an arbitrary number of nested guest layers.
More formally, Popek \& Golberg \cite{Popek:1974:FRV:361011.361073} discussed this subject, introducing the concept of ``recursively virtualizable'' machine and giving an initial definition of recursive virtual machines: If it is possible for a virtual machine to run under itself a copy of the VMM that could also exhibit all the properties of the VMM and this procedure could be repeated until the resources of the systems are consumed, then the original machine is recursively virtualizable.
Moreover, the authors practically defined the features needed by a machine in order to be recursive virtualizable, exploiting concepts of virtualizable architecture and VMM\label{par:form} and introducing a second theorem \cite{Popek:1974:FRV:361011.361073}.

@@

\section{Limits}

@@

\section {MH issues}

@@

\section{Possible architectures}

@@

\section{MH over MH}

@@

\section{MH over GPH}
\label{par:mog}

@@

\section{GPH over MH}
\label{par:gom}

@@

\section{Architecture comparison}

@@

\section{Xen over NOVA}

\paragraph{Inter-platform features}
\paragraph{Tiny TCB}
\paragraph{Leveraging existing APIs}
\paragraph{Fail-safe components architecture}

>>>>

The second class of issues concerns platform integrity and user data privacy. At first, the security architecture of those platform normally does not provide high assurance of privacy. Morevoer, from the point of a cloud provider, it is difficult to observe and inspect deeply the functioning of the whole platform, leveraging commodity general purpose hypervisors (GPH).
General Purpose Hypervisors are executed at the most privileged level and so, it is complicated to detect and intervene on them in presence of malicious attack or misbehavior, without service interruption for all VMs hosted on the server. Cloudvisor \cite{cloudvisor:zhang} analyzed the problem proposing a nested architecture, where the GPH is executed at a lower level of privilege and a tiny hypervisor, responsible to prevent data disclosure, is executed at Ring 0.Hence, this kind of requirements could be called vertical requirements, because they involves layers executed at different layer of the software architecture.

To sum up, nested virtualization has shown to be a interesting pattern for modern cloud platform, that could improve dramatically features and integrity of cloud platform. From this initial analysis it is possible to extract several design principles, reported in table \ref{int:des}

\begin{table}
\label{int:des}
\begin{tabular}{llll}
\toprule
Id & Functional design Principle & Class &\\
\midrule
   DS1 & User-Data privacy & Horizontal & \\
   DS2 & Inter-platform support & Horizontal & \\
   DS3 & Small TCB & Vertical & \\
   DS4 & Fail-Safe modular architecture &  & \\
\bottomrule
      \end{tabular}
\end{table}

\paragraph{Inter-platform support} The cloud architecture has to be designed in order to support directly different platforms and service providers. 
\paragraph{Fail-Safe modular architecture} In order to recover soft failures, the archtecure is supposed to be fail-safe, being able of automatically migrate instances or user-data in presence of a menace, but also reactivating the correct functioning in presence of a software failure. In order to satisfy this property, the amount of safety-critical components has to be as lowest as possible and the overall design has to be kept as modular as possible
\paragraph{Small TCB} The amount of lines of code executed at the highest level of privilege is normally proportional to the number of potential failures and bugs in the platform. According to this, an architecture presenting a tiny TCB will improve its safety and integrity properties by design.
\paragraph{User-Data privacy} The architecture's administrator would not have the right to inspect and analyze user data and instances, without the explicit consensus with the user above mutually trusted services. User-data privacy is a major challenge of modern cloud platforms. It is important to identify a trade-off that allows providers to identify and intervene on possible menaces, but also guarantee the impossibility for a curious or malicious operator to access to them without restrictions.

Moreover, beside this functional design principles specifying which features have to be achieved by the platform, another set of non-functional requirements could be identified. Those requirements concern not directly features or requirements, but the feasibility of the architecture. For example, a major issue could be represented by the amount of code lines that have to be added and maintained to an existing architecture to meet the functional requirement. Even it does not represent a technical limitation to a certain proposal, it could become a ``show-stopper'' factor for its utilization.

\section{Related Work}
Cloud computing feature set could be enlarged exploiting two layers of virtualization instead of just one. The presence of two different hypervisors allows the possibility to specialize hypervisors functions. Instead of having a general purpose hypervisor we could split task in two different layers, interconnected with a well defined interface.
Each layer will have to care about a subset of feautures, simplifying overall development.
However, no architecture had been presented to address vertical and horizontal class of problems at the same time. XenBlanket does not investigate cloud security concerns, limiting the focus on new potential feature of a coordinated multi-provider cloud. Cloudvisor proposed a security architecture that leverages nested virtualization without allowing the possibility of executing more than one nested hypervisor at time, that is a crucial requirements of a multi-provider cloud platform. In fact, in this scenario, each user has to run its own L1 hypervisor instance to enforce a compatibility layer, removing incompatibilities between different providers.

@@

\section{Classic nested virtualization approach}

Recursive virtualization refers to a system architecture with several layers of virtualization. It consists in a ``virtualized'' virtualization, where the guest system virtualize a nested guest. The concept could be generalized to an arbitrary number of nested guest layers.
More formally, Popek \& Golberg \cite{Popek:1974:FRV:361011.361073} discussed this subject, introducing the concept of ``recursively virtualizable'' machine and giving an initial definition of recursive virtual machines: If it is possible for a virtual machine to run under itself a copy of the VMM that could also exhibit all the properties of the VMM and this procedure could be repeated until the resources of the systems are consumed, then the original machine is recursively virtualizable.
Moreover, the authors practically defined the features needed by a machine in order to be recursive virtualizable, exploiting concepts of virtualizable architecture and VMM\label{par:form} and introducing a second theorem \cite{Popek:1974:FRV:361011.361073}.

@@

\subsection{Limits}

@@

\subsection {MH open issues}

@@

\section{Design Principles}

@@

\subsection{MH over MH}

@@

\subsection{MH over GPH}
\label{par:mog}

@@

\subsection{GPH over MH}
\label{par:gom}

@@

\subsection{Architecture comparison}

@@

\section{Implementation}
\subsection{Xen over NOVA}
\paragraph{Inter-platform features}
\paragraph{Tiny TCB}
\paragraph{Leveraging existing APIs}
\paragraph{Fail-safe components architecture}
\subsection{}
